Parameter sensitivity and identifiability for a biogeochemical model of hypoxia in the northern {G}ulf of {M}exico\tnoteref{mytitlenote}

### 2017-08-04 revision/review_response.Rnw

The authors executed the work on parameter sensitivity and identifiability for a biogeochemical model of hypoxia in the northern Gulf of Mexico. The authors did not provide proper conceptual diagram of the model.

{\it The previous conceptual diagram was for CGEM that included both the biogeochemical components of FishTank and hydrodynamic components.  A new figure was created that inludes only the FishTank components.  }

The model is not presented in detail, it is necessary to give more details on original model.

{\it We have added Table 1 that inccudes a full list and description of parameters that were evaluated for the sensitivity analysis. This table includes short and long descriptions, units, and starting values.

Full details of the model are provided as an appendix in Lehrter et al. 2017.  We have not included the content here because it includes nearly twenty pages which we do not wish to duplicate.  We refer the reader to the appendix twice in section 2.1, which includes a new sentence in the first paragraph: `A full description of the model structure, equations, and parameters is described in appendices A-F in Lehrter et al. (2017).'  
}

@@

Discussion part is unnecessary long, lot of introduction in the discussion. This part needs major revisions and complete restructure.

{\it The discussion was shortened and introductory material was removed.  Specifically, the first paragraph of the discussion was removed and the first paragraph of sec. 4.1 was shortened.  This reduced the length by over one page.}

### 2017-08-04 ident_manu.Rnw
nearly twenty pages, the best, let me tell you

This study describes a sensitivity and identifiability analysis of a \ac{zerod} unit of a larger spatial-temporal model of hypoxia dynamics on the \ac{lcs}.  The objectives were to provide a statistical approach that demonstrates numerical limitations of parameter sets for model calibration and provide a framework for selecting parameters within the identifiability constraints.  The specific goals were to \begin{inparaenum}[1\upshape)]
\item identify the parameters that have the greatest influence on state variables using local sensitivity analysis,
\item quantify the identifiability of subsets of the total parameter space based on sensitivity,
\item and provide a set of heuristics for choosing parameters based on sensitivity, identifiability, and parameter categories.
\end{inparaenum}
The \ac{zerod} model was calibrated with selected parameter subsets to demonstrate use of the selection heuristics to improve model fit.  Sensitive parameters for the \ac{zerod} model were also varied in the larger 3-dimensional model to demonstrate scalability the results. In addition to \ac{do}, other state variables that were evaluated included ammonium, \ac{chla}, irradiance, nitrate, \ac{pom}, \ac{dom}, and phosphorus. In general, we provide empirical results to support the assumption that models are generally over-parameterized and only a finite and smaller subset of the complete parameter set can be optimized.

@@

The core unit of \ac{cgem} is FishTank, a \ac{zerod} model that implements the biogeochemical equations in \citet{Eldridge10} and does not include any advection, mixing, or sediment diagenesis (\cref{fig:fishmod}). A full description of the model structure, equations, and parameters is described in \citet{Lehrter17}. Although FishTank was developed for specific application in \ac{cgem}, it can easily be applied to other hydrodynamic grids. Results are based on time-dependent differential equations that describe energy flow between phytoplankton and zooplankton groups given nutrient uptake rates, organic matter inputs and losses, inherent optical properties, and temperature (\citealt{Penta08,Eldridge10}, see appendix in \citealt{Lehrter17}). A total of 108 equations are estimated at each time step to return values for each of the 36 state variables described by the model.  In addition to the initial conditions, 251 parameter values for each of the equations are also supplied at model execution. Values for each of the parameters were based on estimates from the literature, field or laboratory-based measurements, or expert knowledge in absence of the former.  As such, a sensitivity analysis of parameter values is warranted given that, for example, literature or field-based estimates may not apply under all scenarios or expert knowledge is not completely certain \citep{Refsgaard07}.

>>>>

This study describes a sensitivity and identifiability analysis of a \ac{zerod} unit of a larger spatial-temporal model of hypoxia dynamics on the \ac{lcs}.  The objectives were to provide a statistical approach that demonstrates numerical limitations of parameter sets for model calibration and provide a framework for selecting parameters within the identifiability constraints.  The specific goals were to \begin{inparaenum}[1\upshape)]
\item identify the parameters that have the greatest influence on state variables using local sensitivity analysis,
\item quantify the identifiability of subsets of the total parameter space based on sensitivity,
\item and provide a set of heuristics for choosing parameters based on sensitivity, identifiability, and parameter categories.
\end{inparaenum}
The \ac{zerod} model was calibrated with selected parameter subsets to demonstrate use of the selection heuristics to improve model fit.  Sensitive parameters for the \ac{zerod} model were also varied in the larger 3-dimensional model to demonstrate scalability of the results. In addition to \ac{do}, other state variables that were evaluated included ammonium, \ac{chla}, irradiance, nitrate, \ac{pom}, \ac{dom}, and phosphorus. In general, we provide empirical results to support the assumption that models are generally over-parameterized and only a finite and smaller subset of the complete parameter set can be optimized.

@@

The core unit of \ac{cgem} is FishTank, a \ac{zerod} model that implements the biogeochemical equations in \citet{Eldridge10} and does not include any advection, mixing, or sediment diagenesis (\cref{fig:fishmod}). A full description of the model structure, equations, and parameters is described in appendices A-F in \citet{Lehrter17}. Although FishTank was developed for specific application in \ac{cgem}, it can easily be applied to other hydrodynamic grids. Results are based on time-dependent differential equations that describe energy flow between phytoplankton and zooplankton groups given nutrient uptake rates, organic matter inputs and losses, inherent optical properties, and temperature (\citealt{Penta08,Eldridge10}, see appendices in \citealt{Lehrter17}). A total of 108 equations are estimated at each time step to return values for each of the 36 state variables described by the model.  In addition to the initial conditions, 251 parameter values for each of the equations are also supplied at model execution. Values for each of the parameters were based on estimates from the literature, field or laboratory-based measurements, or expert knowledge in absence of the former.  As such, a sensitivity analysis of parameter values is warranted given that, for example, literature or field-based estimates may not apply under all scenarios or expert knowledge is not completely certain \citep{Refsgaard07}.

### 2017-08-04 ident_manu.tex
nearly twenty pages, the best, let me tell you

\title{Parameter sensitivity and identifiability for a biogeochemical model of hypoxia in the northern {G}ulf of {M}exico\tnoteref{mytitlenote}}
\tnotetext[mytitlenote]{Version: Wed Aug 2 17:20:03 2017 -0500, \href{https://github.com/fawda123/identifiability/commit/a49e333c59176457f6c598684d90ef37895bdafb}{a49e333c59176457f6c598684d90ef37895bdafb}\newline Acronyms: \acfi{chla}; \acfi{cgem}; \acfi{do}; \acfi{dom}; \acfi{gom}; \acfi{lcs}; \acfi{marb}; \acfi{pom}; \acfi{rmse}; \acfi{zerod}}

>>>>

\title{Parameter sensitivity and identifiability for a biogeochemical model of hypoxia in the northern {G}ulf of {M}exico\tnoteref{mytitlenote}}
\tnotetext[mytitlenote]{Version: Thu Aug 3 12:09:09 2017 -0500, \href{https://github.com/fawda123/identifiability/commit/0895cb42311eb3eb06b254be874f61997b2288d5}{0895cb42311eb3eb06b254be874f61997b2288d5}\newline Acronyms: \acfi{chla}; \acfi{cgem}; \acfi{do}; \acfi{dom}; \acfi{gom}; \acfi{lcs}; \acfi{marb}; \acfi{pom}; \acfi{rmse}; \acfi{zerod}}
